\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2018-10-21 paper/sp.tex
code
50 percent

In addition, we assume that many entries in the parameter $D$-vector $\theta$ will be zero
(the ``sparsity'' assumption).
In order to represent this expectation,
we optimize not $\chi^2$ but a regularized objective function
\begin{eqnarray}
\hat{\theta} &\leftarrow& \argmin_{\theta}\left[\frac{1}{2}\,\chi^2(\theta) + \lambda\,||P\cdot\theta||_1^1\right]
\label{eq:objective}
\end{eqnarray}
where
$\lambda$ is a regularization parameter,
$P$ is a projection operator that selects out from the $\theta$ vector only those components
that pertain to the \apogee\ spectral pixels,
and $||y||_1^1$ is the L1-norm or sum of absolute values of the components of $y$.
This kind of regularization (L1) adds a convex term to the optimization and leads to
sparse optima.
The $P$ operator makes it such that we only regularize the components of $\theta$ that multiply
the spectral pixels; we ask for the spectral model to be sparse but we don't ask for the photometric
model to be sparse.
We set the value of $\lambda$ by cross-validation.

@@

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$
and uncertainty $\ssigma_m$ for every star $m$.
\tablename~\ref{tab:output} shows a snippet of this catalog of output, with the full catalog available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining our catalog to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \gaia\ Archive (\citealt{gaiaarchive}).
In order to use this output with \apogee\ radial velocities and element abundances, we recommend
joining our catalog to the \sdssiv\ Catalog on the \zmass\ ID (name).

>>>>

In addition, we assume that many entries in the parameter $D$-vector $\theta$ will be zero
(the ``sparsity'' assumption).
In order to represent this expectation,
we optimize not $\chi^2$ but a regularized objective function
\begin{eqnarray}
\hat{\theta} &\leftarrow& \argmin_{\theta}\left[\frac{1}{2}\,\chi^2(\theta) + \lambda\,||P\cdot\theta||_1^1\right]
\label{eq:objective}
\end{eqnarray}
where
$\lambda$ is a regularization parameter,
$P$ is a projection operator that selects out from the $\theta$ vector only those components
that pertain to the \apogee\ spectral pixels,
and $||y||_1^1$ is the L1-norm or sum of absolute values of the components of $y$.
This kind of regularization (L1) adds a convex term to the optimization and leads to
sparse optima.
The $P$ operator makes it such that we only regularize the components of $\theta$ that multiply
the spectral pixels; we ask for the spectral model to be sparse but we don't ask for the photometric
model to be sparse.
We set the value of $\lambda$ by cross-validation across the A/B split (see below).
In the end, the L1 regularization zeros out about 50 percent of the model coefficients.

@@

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$
and uncertainty $\ssigma_m$ for every star $m$.
\tablename~\ref{tab:output} shows a snippet of this catalog of output, with the full catalog available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining our catalog to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \gaia\ Archive (\citealt{gaiaarchive}).
In order to use this output with \apogee\ radial velocities and element abundances, we recommend
joining our catalog to the \sdssiv\ Catalog on the \zmass\ ID (name).
In addition to this catalog, all the code used for this project is available online in an associated
code repository.
